SOURCE SEPARATION METHODS FOR COMPUTER-ASSISTED ORCHESTRATION

### 2021-06-04 source_separation/paper/paper.tex
Add new paragraph for clarity
Add explanation for random orchestra subset

  We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, a target is input to a source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods. The random split of the orchestra is the same for each separation method of the same target. See Fig.~\ref{fig:eval_diagram} for a diagram of this process.

@@

    \subsection{Separation Methods}
  We consider source separation models trained to tackle two distinct separation problems. The first is music source separation (Open-Unmix, Demucs, ConvTasnet). For these architectures, we used models that were pre-trained on the MUSDB18 dataset~\cite{MUSDB18}. Thus, these models output 4 stereo tracks that correspond to broad instrumental categories defined in the SiSEC 2018 Mus evaluation campaign: \textit{vocals, drums, bass} and \textit{other}~\cite{Stoter_SiSEC}. It is important here to make the distinction that we did not train these models ourselves. Therefore, we cannot guarantee that the data the models were trained on is optimal for solving our problem. However, one of the goals of this paper is to explore whether pre-trained music source separation models can separate non-musical sounds in a way that improves orchestration.
  The second type of model we tested are ones that perform universal sound separation (TDCN++, NMF), which \cite{tdcnpp} defines as \textit{separating mixtures of arbitrary sounds of different types}. These methods more closely match our problem of separating non-musical target sounds.

@@

    As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure~\ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. In the full target orchestration, all onsets occur at the beginning of the orchestration. Since there is no knowledge of different sources, Orchidea cannot place the different orchestrations at the appropriate offsets. For the separated orchestrations, the onsets of the sub-target orchestrations can be placed at the correct offset if the separation method has correctly separated out the sources. In the ground truth orchestration, the sources are manually offset, leading to the ground truth having each source orchestration beginning at the correct time. For this reason, despite only performing static orchestrations, the resulting separated and ground truth orchestrations are offset in time compared to the full target orchestration.

@@

    \subsection{Future Work}\label{sec:futurework}  
    As we stated previously, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.

>>>>

  We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, a target is input to a source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods. See Fig.~\ref{fig:eval_diagram} for a diagram of this process.

  For each target, the same random split of the orchestra is used to orchestrate the output of each separation method. We randomly create these subsets of the orchestra in order to avoid any biases that could come from a hand-picking the instruments used to orchestrate each sub-target.

@@

    \subsection{Separation methods}
  We consider source separation models trained to tackle two distinct separation problems. The first is music source separation (Open-Unmix, Demucs, ConvTasnet). For these architectures, we used models that were pre-trained on the MUSDB18 dataset~\cite{MUSDB18}. Thus, these models output 4 stereo tracks that correspond to broad instrumental categories defined in the SiSEC 2018 Mus evaluation campaign: \textit{vocals, drums, bass} and \textit{other}~\cite{Stoter_SiSEC}. It is important here to make the distinction that we did not train these models ourselves. Therefore, we cannot guarantee that the data the models were trained on is optimal for solving our problem. However, one of the goals of this paper is to explore whether pre-trained music source separation models can separate non-musical sounds in a way that improves orchestration.
  The second type of model we tested are ones that perform universal sound separation (TDCN++, NMF), which \cite{tdcnpp} defines as \textit{separating mixtures of arbitrary sounds of different types}. These methods more closely match our problem of separating non-musical target sounds.

@@

    As described in Section \ref{subsec:data}, each target is comprised of four sources that are offset in time to begin playing at different times. Figure~\ref{fig:orchestrations} illustrates the effect this offset has on the full target, separated, and ground truth orchestrations. In the full target orchestration, all onsets occur at the beginning of the orchestration. Since there is no knowledge of different sources, Orchidea cannot place the different orchestrations at the appropriate offsets.

    For the separated orchestrations, the onsets of the sub-target orchestrations can be placed at the correct offset if the separation method has correctly separated out the sources. In the ground truth orchestration, the sources are manually offset, leading to the ground truth having each source orchestration beginning at the correct time. For this reason, despite only performing static orchestrations, the resulting separated and ground truth orchestrations are offset in time compared to the full target orchestration.

@@

    \subsection{Future work}\label{sec:futurework}  
    As we stated previously, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.
